Species richness and network structure jointly drive total biomass and its temporal stability in fish communities

### 2020-09-22 manuscript/bef_stability/manuscript.Rmd
Revision according to Willem comments

- Author affiliation:
  - Alain Danet:
  - Maud Mouchet:
  - Willem Bonnaffe:
  - Elisa Thebault: 
  - Colin Fontaine:

@@

Both the relations between diversity and ecosystem functioning, and between food
web complexity and stability, have received considerable attention during the
last decades in ecology. While the former relation remains rarely investigated
in the context of food webs, especially in empirical studies explicitly
considering food web structures, the latter has been mainly the focus of
theoretical studies and empirical tests are critically missing. Here we link
species richness, food web structure and total biomass and its stability by
using a dataset of standardized fish sampling in French streams running from
1995 to 2018. We inferred trophic interactions thanks to recorded body size and
diet literature. We reveal that species richness and average trophic level had a
positive relationship with total biomass of fish communities while they had
respectively a negative and positive effect on its temporal stability. We
also found that the effects of stream size and temperature on total biomass and
stability are partly mediated by their effects on diversity and food web
structure. Overall, our study opens fruitful perspectives on the link between
species richness, network structure, ecosystem properties and their stability.

@@

Current biodiversity losses and global changes has the potential to affect
ecosystems in complex ways [@bellard_impacts_2012]. Biodiversity has a
tremendous effect on ecosystem properties because it largely determines both the
amount and the distribution of matter and energy fluxes
within and among ecosystems [@duffy_why_2009]. Biodiversity thus affects biomass
production [@tilman_productivity_1996; @cardinale_species_2002;
@grace_integrative_2016], biomass repartition [@thebault_relationship_2006] and
biomass stability [@thebault_trophic_2005; @thebault_relationship_2006;
@tilman_biodiversity_2006]. The relationship between biodiversity and
ecosystem properties is a central topic in ecology [@hector_plant_1999;
@loreau_biodiversity_2001; @hooper_effects_2005; @dunne_network_2006;
@duffy_why_2009; @isbell_forest_quantifying_2018] and its documentation is thus
crucial to better anticipate the impacts of global changes.

@@

Species richness promotes higher biomass production in a variety of ecosystems
and taxons. Indeed species richness generally increases primary productivity and
total biomass in experimental plant communities [@tilman_productivity_1996;
@grace_integrative_2016; @hector_plant_1999; @tilman_biodiversity_2014;
@grace_integrative_2016], but also in briophyte communities
[@mulder_physical_2001], stream feeders [@cardinale_species_2002] and aquatic
bacterial consumers [@pennekamp_biodiversity_2018]. Despite the diversity of
ecosystems and taxons studied, the relation between diversity and ecosystem
functioning remains traditionally focused on single trophic levels, ignoring the
effects of food web structure. Theoretical models have recently extended
classical theoretical studies in plant communities [@tilman_plant_1997;
@loreau_biodiversity_2001] to food webs [@thebault_food-web_2003;
@poisot_dissimilarity_2012; @schneider_animal_2016; @wang_biodiversity_2018].
These models show that both resource use complementarity and selection effects,
the two main mechanisms previously highlighted in single-trophic studies, are
also important to understand diversity effects in food webs
[@thebault_food-web_2003; @poisot_dissimilarity_2012; @schneider_animal_2016].
However, they also reveal new mechanisms such as positive effects of diversity
of trophic levels, i.e. associated with higher trophic levels, on ecosystem
functioning [@wang_biodiversity_2018]. Theoretical studies also showed that food
web properties, such as interaction distribution and strength, affect the
distribution of biomass among adjacent trophic levels
[@thebault_relationship_2006; @schneider_animal_2016; @barbier_pyramids_2019].
Empirical studies are however missing to assess further how food web structure,
in conjunction with species diversity, affect total biomass production and other
ecosystem properties.

@@

Many studies showed that species richness also increases temporal stability of
communities, i.e. variation through time, often quantified by the temporal CV.
Such positive relationships between species richness and temporal stability have
been reported in experimental grasslands and aquatic bacterial systems
[@tilman_biodiversity_2006; @pennekamp_biodiversity_2018] as well as in natural
settings, such as stream fish communities [@franssen_annual_2011], bird and
butterfly communities [@olivier_urbanization_2020]. However, this relation has
been mostly explored in single trophic level systems or without accounting for
food web structure, even more so than the relation between diversity and biomass
production. Single-level theoretical works have clarified which mechanisms
generate this positive relationship between species richness and temporal
stability [@loreau_species_2008; @thibaut_understanding_2013], (1) species
synchrony and (2) species variability. Species synchrony quantify to what extent
the fluctuations of abundances or biomasses through time are correlated among
species. A low synchrony in species fluctuations, i.e.  asynchrony, is
synonymous of compensatory dynamic, where the decrease in abundance of a species
is compensated by the increase of an other.  Asynchrony is generally the main
mechanism whereby species richness has a stabilizing effect on temporal
stability [@tilman_biodiversity_2006; @olivier_urbanization_2020] while
positive, neutral and negative relationships have been found in natural settings
[@tilman_biodiversity_2006; @thibaut_understanding_2013;
@olivier_urbanization_2020]. In addition to diversity, food web structure is
expected to strongly affect the stability of communities and ecosystems, as
outlined by the large body of theoretical studies on this topic [@may_will_1972;
@dunne_network_2006; @neutel_reconciling_2007; @duffy_why_2009;
@stouffer_compartmentalization_2011]. For instance, predation has cascading
effects on species variability [@shanafelt_stability_2018] and it affects as
well synchrony between species [@teng_dynamics_2004]. Despite a long-standing
interest on the links between food web complexity and stability in ecology, to
date we have very few evidence on the relationship between network structure and
the temporal stability of species and total biomass in empirical multitrophic
communities.

@@

Although the relationships between diversity, total biomass and its stability in
natural systems can be similar to those found in experimental communities [e.g.,
@wu_relationship_2015; @li_relationship_2018], negative or non significant
effects of species richness on total biomass have for example been found in some
natural communities such as forests [@szwagrzyk_above-ground_2007;
@jacob_productivity_2010; @seidel_relationship_2013]. Some authors suggest that
the lack of resource complementarity or environmental harshness might be
responsible for an absence or a negative effect of species richness
[@loreau_biodiversity_2001; @he_global_2013; @wu_relationship_2015]. These
different relations might also arise from effects of the environment on both
diversity and ecosystem functions [@loreau_biodiversity_2001].

@@

When assessing the relationship between community structure and ecosystem
properties in natural communities, it is indeed crucial to consider
environmental factors [@loreau_biodiversity_2001; @he_global_2013;
@grace_integrative_2016]. Environment affects organism performance directly, and
thereby, species abundances, total biomass [@grace_integrative_2016] and temporal
stability [@de_boeck_patterns_2017; @hansen_climate_2013; @bluthgen_land_2016;
@oliver_heterogeneous_2010; @franssen_annual_2011; @friedpetersen_drivers_2020].
For example, greater ecosystem size might increase the number of available
resources and thus total biomass [@post_ecosystem_2000; @doi_resource_2009].
@li_relationship_2018 have notably shown that climate moisture has a positive
direct effect on total biomass, but also indirect through a positive effect on
species richness. Accounting for environment also allow for an overall
comparison of the strength of the effects of environment and community structure
on total biomass and its stability.

@@

Because their trophic interactions can be inferred, stream fish community
constitutes a good model to study the effects of network structure on total
biomass and its temporal stability. Despite that fish trophic
interactions are difficult to measure in natural conditions, a consequent body
of literature supports that they can be inferred through body size and diet
informations [@gravel_inferring_2013; @jennings_weak_2001;
@brose_predator_2019]. Especially in stream communities, including fishes,
@brose_predator_2019 found that the prediction of predator prey trophic
interactions based on body size ratio was far better in stream ecosystems than
in other aquatic and terrestrial ecosystems. Furthermore, the biotic activity in
stream ecosystems determines for a large part the water quality
[@cummins_structure_1974] and thus are crucial to maintain stream ecosystem
properties. Lastly, most of the diversity-biomass and diversity-stability
relationships, have been assessed in terrestrial ecosystems while there is a
evident need to test such relationships in a variety of ecosystem types.

Our study aims to document the relationships between food web structure and
total biomass and its temporal stability in natural communities. To do so, we
used the ONEMA dataset consisting in standardized sampling of fish communities
in French streams [@edeline_ecological_2013]. 99 sites were sampled for more than 10
years spanning on the 1995-2018 period. We inferred 1496 interaction networks,
based on body size and food diet. We question whether species richness,
connectance and average trophic level increase, decrease or are not related to
total biomass and its temporal stability. We further question whether the
species richness, connectance and average trophic level have antagonistic or
synergistic effect on total biomass and its temporal stability. Finally, we
question if ecosystem size and average temperature increase total biomass and
its temporal stability.

@@

The body size of all fish individuals was not recorded when they were too
numerous. The body size of the unmeasured individuals was inferred under the
assumption that species body size followed a normal distribution whose mean and
standard deviation were quantified from the recorded individuals of the sampling
(See supplementary methods, Figure S1). The body mass of each individual was
then estimated using an allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$
being the body mass in grams, $l$ the body size in millimeters and $i$ the
individual), where the coefficients $0.01$ and $3.03$ comes from two
meta-analyses on fishes [@lleonart_removing_2000; @froese_cube_2006]. Species
biomass and total biomass at each sampling event was then calculated by summing
individual body masses. To account for the variation in sampling effort among
sites, species biomass and total biomass have been related to the surface
sampled, i.e.  $gm^{-2}$. In the further analysis, the total biomass of a
station has been defined as the median of the total biomass over time.

@@

In order to describe the mechanisms driving the temporal stability of biomass, we
decomposed the $CV$ of total biomass ($CV_{com}$) in synchrony ($\phi$) and
weighted average species $CV$ ($\overline{CV_{sp}}$) components according to
@thibaut_understanding_2013:

@@

Species richness was computed as the total number of species present over time
in a given station. As for biomass, we controlled species richness for sampling
effort by dividing the total number of species by the total surface sampled in
the given station. Species richness was then expressed in number of species by
square meter sampled.

@@

We determined the network structure in two steps: (1) build a metaweb describing the
trophic interactions between all trophic species and the resources (Figure
\@ref(fig:matmet) C), then (2) determine network of a given community by
subtracting the metaweb according to the trophic species present in a given
site and sampling event (Figure \@ref(fig:matmet) D).

Trophic interaction network was inferred from body size and ontogenic diet shift
following previous studies [@gravel_inferring_2013; @brose_predator_2019;
@poisot_structure_2016]. The diet of stream fishes, as many organisms, shifts
over lifespan and thereby over body size. For example, alvins feed on plankton
while adults may feed on algae, fishes, with bigger individuals eating bigger
fishes. Each fish species was hence divided in nine body size classes, each
corresponding to a trophic species (Figure S2). Additionally to the fish trophic
species, we added seven resource nodes present in the ontogenic food diet database:
detritus, biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and
zoobenthos (grey nodes in Figure \@ref(fig:matmet) C & D). The fish trophic
species and the resources constituted the 412 nodes of the metaweb, 45 fish
species divided into nine body classes plus seven resource nodes. The inference
of trophic interactions was shown to be more accurate when considering body size
classes, i.e. trophic species, rather than species [@jennings_weak_2001].

The feeding interactions of a fish node, i.e a trophic species, are determined
by both its species identity and its body size. Then, species identity allows to
differentiate between piscivorous and non piscivorous species, to know on which
resources the trophic species are feeding on and to know the minimum size at
which a piscivorous species begins to feed on fishes. The ontogenic fish diet
database was filled according to fishbase and literature (cf Bonnaffe ref). Each
fish species had two or three life stages which are delimited by a body size
range (Figure S2). The life stage of a fish trophic species was determined with
the center of its body size range, hereafter midpoint (Figure S2).

@@

For each trophic network, corresponding to a particular site and year, we
computed two of the most commonly used network metrics to characterize food
webs, namely the connectance and mean trophic level. 
As the networks, the networks metrics were also based on the trophic species,
i.e. body size classes. Connectance describes the level of generalism in the
network and is calculated as the number of actual
interaction divided by the maximum number of interaction if all species interact
together ($C = L / N^2$, L and N being resp. the number of links and of trophic
species plus resource nodes). The mean trophic level $\overline{T}$ was computed
as the mean trophic level weighted by the biomass of each trophic species
(excluding resource nodes for which we had no biomass information), so
$\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, with $T_i$ and
$B_i$ being respectively the trophic level and the biomass of the node $i$. The
trophic level of the nodes was computed as one added to the average trophic
level of its food item. For each site, the median of connectance and average
trophic level over time was used in subsequent analysis.

@@

Structural Equation Modeling are able to assess multivariate relationships
between variables. It is one promising way to go beyond bivariate relationships
and to investigate complex relationships, direct and
indirect, between variables [@grace_structural_2008; @grace_causal_2014;
@lefcheck_piecewisesem_2016; @grace_integrative_2016]. The structural equation
model explaining the annual total biomass set that environment
can directly affect species richness and network structure, as well as annual total
biomass (Figure \@ref(fig:sem-plot) B). We assumed that both species richness
and network structure directly affect total biomass (Figure \@ref(fig:sem-plot)
B) and that species richness constrained food web structure
[@winemiller_must_1989; @dunne_network_2006; @thebault_stability_2010].

We used the same model structure for temporal stability of biomass (Figure
\@ref(fig:sem-plot) A). Instead of the annual total biomass, we set the
synchrony and population variability which in turn determined the temporal
stability of biomass. The structural equation models used for annual total
biomass and its temporal stability contains respectively 4 and 6 response
variables, 35 and 26 direct paths.

@@

The indirect effects of variables on total biomass and its temporal stability
was computed by multiplying slopes along the path. As an example, if we consider
$A \to B \to C$, the indirect effect of A on C is equal to $r_{AB} \times
r_{BC}$.  Only significant direct slopes were entered in the calculation of
indirect effects. Finally total effects were computed as the sum
of direct and indirect effects.

@@

The two PCA axis capturing environmental variables had no significant direct effects on total biomass
(Table SXX), but indirect (Table \@ref(tab:indir-sem)). The first axis, PCA1,
related to the stream size was positively linked to total biomass ($r_\delta = 
`r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-sem)),
through species richness and mean trophic level too ($r_\delta = 
`r env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_com["log_RC1"]`$
resp., Table \@ref(tab:indir-sem)). The second axis, PCA2, related the average
annual temperature and reversely to altitude of the sites was positively related
to total biomass ($r_\delta = `r env_on_bm$total["log_RC2"]`$, Table
\@ref(tab:indir-sem)), mainly through species richness ($r_\delta = 
`r env_on_bm$via_richness["log_RC2"]`$, Table \@ref(tab:indir-sem)). The effect
of PCA2 on total biomass was of the same magnitude than the effects on species
richness and mean trophic level.

@@

The total effect of mean trophic level on temporal stability of biomass was of
the same magnitude than the one of species richness (resp.
$`r com_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
\@ref(tab:indir-sem)).
The mean trophic level had only a direct negative effect on
$\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
Figure \@ref(fig:sem-plot) C) and thereby had a total positive
effect on temporal stability ($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$,
Table \@ref(tab:indir-sem)). Connectance had no significant direct on either
$\overline{CV_{sp}}$ nor synchrony and thus no effect on temporal stability
(Figure \@ref(fig:sem-plot) C, Table SXX).

The total effect of PCA2, related to average annual temperature and reversely to
altitude, on temporal stability was of higher magnitude than the effects of
species richness and mean trophic level (Table
\@ref(tab:indir-sem)).
The PCA2 had a total negative effect on temporal stability, meaning that higher
temperature results in lower stability
($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-sem)). 
PCA2 had an indirect positive effect on temporal stability through a
direct positive effect on $\overline{CV_{sp}}$ ($r_\delta = 
`r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-sem)) but also a
negative on through species richness but a positive one through
mean trophic level
(resp. $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$ and
$r_\delta = `r env_on_stab$via_com["log_RC2"]`$, Table \@ref(tab:indir-sem)).
This was also true for the PCA1, related to stream size, but effects were weaker
than for PCA2.

@@

Overall, our study is unique by its level of integration, from environmental
effects to total biomass and stability, going through species richness and
network structure, and the first direct assessment of a possible joint effect of
species richness and network structure.  We found that species richness and mean
trophic level had a positive effect on total biomass. In contrast, species
richness had a negative effect on temporal stability whereas mean trophic level
covaried positively. We also found that the effect of species richness and mean
trophic level on total biomass and its temporal stability were not independant
as species richness had a negative effect on mean trophic level.  Furthermore,
we found that connectance had no significant effect on both total biomass and
its temporal stability. Finally, we found that the magnitude of the effects of
average temperature and altitude was equal or superior to the effects of species
richness and mean trophic level.

@@

We found that species richness increased total biomass as found in salt marshes,
grasslands and forests [@hector_plant_1999; @tilman_biodiversity_2014;
@wu_relationship_2015; @li_relationship_2018]. The positive effect of species
richness on total biomass might be due to resource use complementarity
[@carey_determining_2011], which is held by niche differentiation
[@loreau_biodiversity_1998; @loreau_partitioning_2001] or to the higher
probability to get high biomass species  with higher species richness
[@loreau_biodiversity_2001].

>>>>

- Author affiliation:
  - Alain Danet:
  - Maud Mouchet:
  - Willem Bonnaffe: Ecological and Evolutionary Dynamics Lab. Zoology Research
    and Administration Building, 11a Mansfield Rd, Oxford OX1 3SZ, United
    Kingdom.
  - Elisa Thebault: 
  - Colin Fontaine:

@@

Both the relationship between diversity and ecosystem functioning, and that between food
web complexity and stability, have received considerable attention during the
last decades in ecology. The former relationship remains rarely investigated
in the context of food webs, especially in empirical studies explicitly
considering food web structures, the latter has been mainly the focus of
theoretical studies and empirical tests are critically missing. Here we link
species richness, food web structure and total biomass and its stability by
using a dataset of standardized fish sampling in French streams running from
1995 to 2018. We inferred trophic interactions thanks to recorded body size and
diet literature. We reveal that species richness and average trophic level had a
positive relationship with total biomass of fish communities while they had
respectively a negative and positive effect on its temporal stability. We
also found that the effects of stream size and temperature on total biomass and
stability are partly mediated by their effects on diversity and food web
structure. Overall, our study opens fruitful perspectives on the link between
species richness, network structure, ecosystem properties and their stability.

@@

Current biodiversity losses and global changes has the potential to affect
ecosystems in complex ways [@bellard_impacts_2012]. Biodiversity has a
tremendous effect on ecosystem properties because it largely determines both the
amount and the distribution of matter and energy fluxes
within and among ecosystems [@duffy_why_2009]. Biodiversity thus affects biomass
production [@tilman_productivity_1996; @cardinale_species_2002;
@grace_integrative_2016], distribution [@thebault_relationship_2006] and
stability [@thebault_trophic_2005; @thebault_relationship_2006;
@tilman_biodiversity_2006]. The relationship between biodiversity and
ecosystem properties is a central topic in ecology [@hector_plant_1999;
@loreau_biodiversity_2001; @hooper_effects_2005; @dunne_network_2006;
@duffy_why_2009; @isbell_forest_quantifying_2018] and its documentation is thus
crucial to better anticipate the impacts of global change.

@@

Species richness promotes higher biomass production in a variety of ecosystems
and taxons. Indeed species richness generally increases primary productivity and
total biomass in experimental plant communities [@tilman_productivity_1996;
@grace_integrative_2016; @hector_plant_1999; @tilman_biodiversity_2014;
@grace_integrative_2016], but also in briophyte communities
[@mulder_physical_2001], stream feeders, [@cardinale_species_2002] and aquatic
bacterial consumers [@pennekamp_biodiversity_2018]. Despite the diversity of
ecosystems and taxons studied, the relationship between diversity and ecosystem
functioning remains traditionally focused on single trophic levels, ignoring the
effects of food web structure. Theoretical models have recently extended
classical theoretical studies in plant communities [@tilman_plant_1997;
@loreau_biodiversity_2001] to food webs [@thebault_food-web_2003;
@poisot_dissimilarity_2012; @schneider_animal_2016; @wang_biodiversity_2018].
These models show that both resource use complementarity and selection effects,
the two main mechanisms previously highlighted in single-trophic studies, are
also important to understand diversity effects in food webs
[@thebault_food-web_2003; @poisot_dissimilarity_2012; @schneider_animal_2016].
However, they also reveal new mechanisms such as positive effects of diversity
of trophic levels, i.e. associated with higher trophic levels, on ecosystem
functioning [@wang_biodiversity_2018]. Theoretical studies also showed that food
web properties, such as interaction distribution and strength, affect the
distribution of biomass among adjacent trophic levels
[@thebault_relationship_2006; @schneider_animal_2016; @barbier_pyramids_2019].
We are lacking empirical studies that assess jointly how food web structure, in
conjunction with species diversity, affect total biomass production and other
ecosystem properties.

@@

Many studies showed that species richness increases temporal stability of
communities, i.e. variation through time, often quantified by the temporal CV.
Such positive relationships between species richness and temporal stability have
been reported in experimental grasslands and aquatic bacterial systems
[@tilman_biodiversity_2006; @pennekamp_biodiversity_2018] as well as in natural
settings, such as stream fish communities [@franssen_annual_2011], bird and
butterfly communities [@olivier_urbanization_2020]. However, this relationship has
been mostly explored in single trophic level systems or without accounting for
food web structure, even more so than the relationship between diversity and biomass
production. Several theoretical studies at considering single trophic level have clarified which mechanisms
generate this positive relationship between species richness and temporal
stability [@loreau_species_2008; @thibaut_understanding_2013], (1) species
synchrony and (2) species variability. Species synchrony captures to what extent
the fluctuations of abundances or biomasses through time are correlated among
species. A low synchrony in species fluctuations, i.e. asynchrony, is
synonymous of compensatory dynamic, where the decrease in abundance of a species
is compensated by the increase of an other.  Asynchrony is generally the main
mechanism which species richness has a stabilizing effect on temporal
stability [@tilman_biodiversity_2006; @olivier_urbanization_2020].Though most often positive, the relationship between species diversity and asynchrony has also been evidenced to be neutral or negative in natural settings
[@tilman_biodiversity_2006; @thibaut_understanding_2013;
@olivier_urbanization_2020]. In addition to diversity, food web structure is
expected to strongly affect the stability of communities and ecosystems, as
outlined by the large body of theoretical studies on this topic [@may_will_1972;
@dunne_network_2006; @neutel_reconciling_2007; @duffy_why_2009;
@stouffer_compartmentalization_2011]. In particular, predation has cascading
effects on both species variability and synchrony [@teng_dynamics_2004; @shanafelt_stability_2018] and it affects as
well synchrony between species. In spite a long-standing interest for the links between food web complexity and stability in ecology, to
date we have very few evidence on the relationship between network structure and
the temporal stability of species and total biomass in empirical multitrophic
communities.

@@

Although the relationships between diversity, total biomass and its stability in
natural systems can be similar to those found in experimental communities [e.g.,
@wu_relationship_2015; @li_relationship_2018], negative or non significant
effects of species richness on total biomass have for example been found in some
natural communities such as forests [@szwagrzyk_above-ground_2007;
@jacob_productivity_2010; @seidel_relationship_2013]. Some authors suggest that
the lack of resource complementarity or environmental harshness might be
responsible for negligible, or negative effects of species richness
[@loreau_biodiversity_2001; @he_global_2013; @wu_relationship_2015]. These
different relationships might also arise from effects of the environment on both
diversity and ecosystem functions [@loreau_biodiversity_2001].

@@

Environmental effects might also complicate (or obscure) the relationship
between diversity and structure in driving stability and biomass in natural
systems [@loreau_biodiversity_2001; @he_global_2013;
@grace_integrative_2016]. Environment affects organism performance directly, and
thereby, species abundances, total biomass [@grace_integrative_2016] and temporal
stability [@de_boeck_patterns_2017; @hansen_climate_2013; @bluthgen_land_2016;
@oliver_heterogeneous_2010; @franssen_annual_2011; @friedpetersen_drivers_2020].
For example, larger ecosystem might increase the number of available
resources and thus total biomass [@post_ecosystem_2000; @doi_resource_2009].
@li_relationship_2018 have notably shown that climate moisture has a positive
direct effect on total biomass, but also indirect through a positive effect on
species richness. Accounting for environment also allow for an overall
comparison of the strength of the effects of environment and community structure
on total biomass and its stability.

@@

Because their trophic interactions can be inferred, stream fish communities
constitute a good model to study the effects of network structure on total
biomass and its temporal stability. Despite that fish trophic
interactions are difficult to measure in natural conditions, a substantial body
of literature supports that they can be inferred through body size and diet
informations [@gravel_inferring_2013; @jennings_weak_2001;
@brose_predator_2019]. Especially in stream communities, including fishes,
@brose_predator_2019 found that the prediction of predator prey trophic
interactions based on body size ratio was far better in stream ecosystems than
in other aquatic and terrestrial ecosystems. Lastly, most of the diversity-biomass and diversity-stability
relationships, have been assessed in terrestrial ecosystems while there is a
evident need to test such relationships in a variety of ecosystem types.

Our study aims to document the relationships between food web structure and
total biomass and its temporal stability in natural communities. To do so, we
used the ONEMA dataset consisting in standardized sampling of fish communities
in French streams [@edeline_ecological_2013]. 99 sites were sampled for more than 10
years spanning on the 1995-2018 period. We inferred 1496 interaction networks,
based on body size and diet. We question whether species richness,
connectance and average trophic level increase, decrease or are not related to
total biomass and its temporal stability. We further question whether the
species richness, connectance, and average trophic level have antagonistic or
synergistic effect on total biomass and its temporal stability. Finally, we
question if ecosystem size and average temperature increase total biomass and
its temporal stability.

@@

The body size of all fish individuals was not recorded when they were too
numerous. The body size of the unmeasured individuals was inferred under the
assumption that species body size followed a normal distribution whose mean and
standard deviation were quantified from the recorded individuals of the sampling
(See supplementary methods, Figure S1). The body mass of each individual was
then estimated using an allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$
being the body mass in grams, $l$ the body size in millimeters and $i$ the
individual), where the coefficients $0.01$ and $3.03$ comes from two
meta-analyses on fishes [@lleonart_removing_2000; @froese_cube_2006]. Species
biomass and total biomass at each sampling event was then calculated by summing
individual body masses. To account for the variation in sampling effort among
sites, species biomass and total biomass have been related to the surface
sampled, i.e.  $gm^{-2}$. In the analysis, the total biomass of a
station has been defined as the median of the total biomass acrossall times.

@@

In order to describe the mechanisms driving the temporal stability of biomass, we
decomposed the $CV$ of total biomass ($CV_{com}$) into a synchrony ($\phi$) and
a
weighted average species $CV$ ($\overline{CV_{sp}}$) components according to
@thibaut_understanding_2013:

@@

Species richness was computed as the total number of species present across all times
in a given station. As for biomass, we controlled species richness for sampling
effort by dividing the total number of species by the total surface sampled in
the given station. Species richness was then expressed in number of species by
square meter sampled.

@@

We determined the network structure in two steps: (1) build a metaweb describing the
trophic interactions between all trophic species and the resources (Figure
\@ref(fig:matmet) C), then (2) determine network of a given community by
extracting the metaweb according to the trophic species present at a given
site and sampling event (Figure \@ref(fig:matmet) D).

Trophic interaction network was inferred from body size and ontogenic diet shift
following previous studies [@gravel_inferring_2013; @brose_predator_2019;
@poisot_structure_2016]. The diet of stream fishes, as many organisms, shifts
throughout an individual's life, and thereby with body size. For example, alvins
feed on plankton while adults may feed on algae, fishes, with bigger individuals
eating bigger
fishes. Each fish species was hence divided in nine body size classes, each
corresponding to a trophic species (Figure S2). Additionally to the fish trophic
species, we added seven resource nodes present in the ontogenic food diet database:
detritus, biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and
zoobenthos (grey nodes in Figure \@ref(fig:matmet) C & D). The fish trophic
species and the resources constituted the 412 nodes of the metaweb, 45 fish
species divided into nine body size classes plus seven resource nodes. The inference
of trophic interactions was shown to be more accurate when considering body size
classes, i.e. trophic species, rather than species [@jennings_weak_2001].

The feeding interactions of a fish node, i.e a trophic species, were determined
by both its species identity and its body size. Then, species identity allowed to
differentiate between piscivorous and non piscivorous species, to know which
resources the trophic species are feeding on and to know the minimum size at
which a piscivorous species begin to feed on fishes. The ontogenic fish diet
database was filled according to fishbase and literature (cf Bonnaffe ref). Each
fish species had two or three life stages which are delimited by a body size
range (Figure S2). The life stage of a fish trophic species was determined with
the center of its body size range, hereafter midpoint (Figure S2).

@@

For each trophic network, corresponding to a particular site and year, we
computed two of the most commonly used network metrics to characterize food
webs, namely the connectance and mean trophic level. 
The networks metrics were also based on the trophic species,
i.e. body size classes. Connectance describes the level of generalism in the
network and is calculated as the actual number of
interactions divided by the maximum number of interactions if all species interact
together ($C = L / N^2$, L and N being resp. the number of links and of trophic
species plus resource nodes). The mean trophic level $\overline{T}$ was computed
as the mean trophic level weighted by the biomass of each trophic species
(excluding resource nodes for which we had no biomass information), so
$\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, with $T_i$ and
$B_i$ being respectively the trophic level and the biomass of the node $i$. The
trophic level of the nodes was computed as one added to the average trophic
level of its food item. For each site, the median of connectance and average
trophic level over time was used in subsequent analysis.

@@

Structural Equation Modeling enables us to assess multivariate relationships
between variables. It is a promising way to go beyond bivariate relationships
and to investigate complex relationships, direct and
indirect, between variables [@grace_structural_2008; @grace_causal_2014;
@lefcheck_piecewisesem_2016; @grace_integrative_2016]. The structural equation
model explaining the annual total biomass allowed the environment
to affect directly species richness and network structure, as well as annual total
biomass (Figure \@ref(fig:sem-plot) B). We assumed that both species richness
and network structure directly affect total biomass (Figure \@ref(fig:sem-plot)
B) and that species richness affected food web structure
[@winemiller_must_1989; @dunne_network_2006; @thebault_stability_2010].

We used the same model structure for temporal stability of biomass (Figure
\@ref(fig:sem-plot) A). Instead of the annual total biomass, we modelled the
synchrony and population variability which in turn determined the temporal
stability of biomass. The structural equation models used for annual total
biomass and its temporal stability contained respectively 4 and 6 response
variables, 35 and 26 direct paths.

@@

Indirect effects on total biomass and its temporal stability
were computed by multiplying slopes along the path. As an example, if we consider
$A \to B \to C$, the indirect effect of A on C is equal to $r_{AB} \times
r_{BC}$.  Only significant direct slopes were entered in the calculation of
indirect effects. Finally total effects were computed as the sum
of direct and indirect effects.

@@

The two PCA axis capturing environmental variables had no significant direct effects on total biomass
(Table SXX), but indirect (Table \@ref(tab:indir-sem)). The first axis, PCA1,
related to the stream size was positively linked to total biomass ($r_\delta = 
`r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-sem)),
through species richness and mean trophic level too ($r_\delta = 
`r env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_com["log_RC1"]`$
resp., Table \@ref(tab:indir-sem)). The second axis, PCA2, related to the average
annual temperature and inversely to altitude of the sites was positively related
to total biomass ($r_\delta = `r env_on_bm$total["log_RC2"]`$, Table
\@ref(tab:indir-sem)), mainly through species richness ($r_\delta = 
`r env_on_bm$via_richness["log_RC2"]`$, Table \@ref(tab:indir-sem)). The effect
of PCA2 on total biomass was of the same magnitude than the effects on species
richness and mean trophic level.

@@

The total effect of mean trophic level on temporal stability of biomass was of
the same magnitude than the one of species richness (resp.
$`r com_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
\@ref(tab:indir-sem)).
The mean trophic level had only a direct negative effect on
$\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
Figure \@ref(fig:sem-plot) C) and thereby had a total positive
effect on temporal stability ($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$,
Table \@ref(tab:indir-sem)). Connectance had no significant direct effect on either
$\overline{CV_{sp}}$ nor synchrony and thus no effect on temporal stability
(Figure \@ref(fig:sem-plot) C, Table SXX).

The total effect of PCA2, related to average annual temperature and inversely to
altitude, on temporal stability was of higher magnitude than the effects of
species richness and mean trophic level (Table
\@ref(tab:indir-sem)).
The PCA2 had a total negative effect on temporal stability, meaning that higher
temperature results in lower stability
($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-sem)). 
PCA2 had an indirect positive effect on temporal stability through a
direct positive effect on $\overline{CV_{sp}}$ ($r_\delta = 
`r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-sem)) but also a
negative one through species richness but a positive one through
mean trophic level
(resp. $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$ and
$r_\delta = `r env_on_stab$via_com["log_RC2"]`$, Table \@ref(tab:indir-sem)).
This was also true for the PCA1, related to stream size, but effects were weaker
than for PCA2.

@@

Overall, our study is unique by its level of integration, from environmental
effects to total biomass and stability, going through species richness and
network structure, and the first direct assessment of a possible joint effect of
species richness and network structure on both total biomass and its temporal
stability. We found that species richness and mean
trophic level had a positive effect on total biomass. In contrast, species
richness had a negative effect on temporal stability whereas mean trophic level
covaried positively. We also found that the effect of species richness and mean
trophic level on total biomass and its temporal stability were not independant
as species richness had a negative effect on mean trophic level.  Furthermore,
we found that connectance had no significant effect on both total biomass and
its temporal stability. Finally, we found that the magnitude of the effects of
average temperature and altitude was equal or superior to the effects of species
richness and mean trophic level.

@@

We found that species richness increased total biomass as found in salt marshes,
grasslands and forests [@hector_plant_1999; @tilman_biodiversity_2014;
@wu_relationship_2015; @li_relationship_2018]. The positive effect of species
richness on total biomass might be due to resource use complementarity
[@carey_determining_2011], which is held by niche differentiation
[@loreau_biodiversity_1998; @loreau_partitioning_2001] or to the higher
probability of getting high biomass species with higher species richness
[@loreau_biodiversity_2001].

Surprisingly we found a negative relationship between temporal stability and
species richness. Overall, it contrasts with experimental studies in grasslands
[@tilman_biodiversity_2006]; mesocosms (Pennekamp et al. 2018), in 
butterflies natural communities [@olivier_urbanization_2020] or even in lotic
fish communities [@franssen_annual_2011] where positive relationships were found
between temporal stability and species richness. However, other studies found an
opposite relationship in natural grassland [@yang_effects_2011] and a marginal
one in natural forests [@declerck_species_2006].
